Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-26 Dissertation/Thesis/tex/multivehicle.tex
updated & edited up to 5.2.2 (no patrol simulation yet)

\section{Bidding-Based Autonomous Exploration}

@@

During this chapter, we assume a 3D vertically-uniform environment at a fixed exploration height as described in Chapter \ref{chap:ae3Dsimple} using the 2D projected combination map $m_\text{2D}$. Then information gain is based on \refeqn{ObjFun} and \refeqn{ObjFunApprox}, and depends on this reduced map only, i.e.,
\begin{align}
\label{eqn:expectedInfoGainMap2D}
\mathcal I(X_c,m_\text{2D})&=H(P(m_\text{2D}))-\text{E}\left[H(P(m|X_c,Z_c))\right],
\end{align}
where the expected scan $Z$ is given from \refeqn{expectedInfoGainRay} and \refeqn{FindRc}.

@@

	\begin{figure}
		\centerline{
			\includegraphics[width=0.9\columnwidth]{NonZeroBump.pdf}
		}
		\caption{The bump function is designed to promote travel distances close to $d_\text{opt}$ by multiplying this function by the expected information gain objective. Travel distances less than $d_\text{opt}$ are below the robot capabilities. Travel distances beyond $d_\text{opt}$ are beyond what the robot can reach within the minimum exploration computation time.}
		\label{fig:nonzeroBumpFun}
	\end{figure}

@@

The first step between auctions is to modify the expected map information gain for efficient map coverage.  Once a robot wins a bid, the measurement ray expected values serve to update a temporary copy of $m_\text{2D}$, namely $m_\text{2D,copy}$, and those candidates located in a local neighborhood (twice the radius of a maximum sensor reading) of the winning candidate from the prior auction are recalculated, thereby coordinating total map information gain with auction-winning robots. Using the same local map notation from \refeqn{allEta} and \refeqn{Unnormalized} along a measurement ray, the expected measurement value is
\begin{align}
\label{eqn:ExpectedMeasRay}
\text{E}[z]=\sum_{k=1}^{n_{r}}\bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{m}}_j)\bigg\}P(\mathbf{m}_k)z_k,
\end{align}
where $z_k$ denotes the distance from the robot sensor to the $k$-th cell along the measurement ray. Then $\text{E}[z]$ is substituted into \refeqn{RayISMAnswer}--\refeqn{allEta} to modify $m_\text{2D,copy}$, and expected map information gains are recomputed with \refeqn{ProbMeas} and \refeqn{expectedInfoGainRay}, while the bump function \refeqn{BumpFun} remains the same. In short, the expected changes of $m_\text{2D}$ are integrated into $m_\text{2D,copy}$ for expected information gain estimation between multiple vehicles.

@@

@@

\subsection{Continuous-Time Markov Process for Cell Degradation}
% JINT18 fig. 3

>>>>

\section{Bidding-Based Autonomous Exploration}
\label{sec:BiddingExploration}

@@

During this chapter, we assume a 3D vertically-uniform environment at a fixed exploration height as described in Chapter \ref{chap:ae3Dsimple} using the 2D projected combination map $ m_\text{2D}$. Then information gain is based on \refeqn{ObjFun} and \refeqn{ObjFunApprox}, and depends on this reduced map only, i.e.,
\begin{align}
\label{eqn:expectedInfoGainMap2D}
\mathcal I(X_c,m_\text{2D})&=H(P(m_\text{2D}))-\text{E}\left[H(P(m|X_c,Z_c))\right],
\end{align}
where the expected scan $Z$ is given from \refeqn{expectedInfoGainRay} and \refeqn{FindRc}.

@@

	\begin{figure}
		\centering{
			\includegraphics[width=0.9\columnwidth]{NonZeroBump.pdf}
		}
		\caption{The bump function is designed to promote travel distances close to $d_\text{opt}$ by multiplying this function by the expected information gain objective. Travel distances less than $d_\text{opt}$ are below the robot capabilities. Travel distances beyond $d_\text{opt}$ are beyond what the robot can reach within the minimum exploration computation time.}
		\label{fig:nonzeroBumpFun}
	\end{figure}

@@

The first step between auctions is to modify the expected map information gain for efficient map coverage.  Once a robot wins a bid, the measurement ray expected values serve to update a temporary copy of $ m_\text{2D}$, namely $ m_\text{2D,copy}$, and those candidates located in a local neighborhood (twice the radius of a maximum sensor reading) of the winning candidate from the prior auction are recalculated, thereby coordinating total map information gain with auction-winning robots. Using the same local map notation from \refeqn{allEta} and \refeqn{Unnormalized} along a measurement ray, the expected measurement value is
\begin{align}
\label{eqn:ExpectedMeasRay}
\text{E}[z]=\sum_{k=1}^{n_{r}}\bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{m}}_j)\bigg\}P(\mathbf{m}_k)z_k,
\end{align}
where $z_k$ denotes the distance from the robot sensor to the $k$-th cell along the measurement ray. Then $\text{E}[z]$ is substituted into \refeqn{RayISMAnswer}--\refeqn{allEta} to modify $ m_\text{2D,copy}$, and expected map information gains are recomputed with \refeqn{ProbMeas} and \refeqn{expectedInfoGainRay}, while the bump function \refeqn{BumpFun} remains the same. In short, the expected changes of $ m_\text{2D}$ are integrated into $ m_\text{2D,copy}$ for expected information gain estimation between multiple vehicles.

@@

The algorithms for mapping, exploration, and visualization are designed for the ROS framework. This framework allows the node that computes 3D mapping probabilities to easily transfer these to an exploration node and a visualization node. However, unlike the simulation in Section \ref{sec:Compare2MapProjections}, scalability to larger environment is necessary. For this task, the exploration node is separated into three threads running in parallel. The first thread constantly updates the 2D projected map according to \refeqn{CombinationProjection2DMap}. The second thread computes the information gains, runs auctions, and generates trajectories. The third thread broadcasts a message for visualizing the 2D projected map. This structure is chosen because the 2D map cannot afford to miss messages, and the last two may produce time bottlenecks and are independent of each other. The final node is for 3D map visualization, and it creates a message to the ROS visualization package, Rviz, to produce 3D cells with varying opacities corresponding to cell occupancy probabilities.

The multi-vehicle exploration problem is typically applied to large environments, so several additional scalability precautions are taken to avoid large communications and computations. Most importantly, only the map \emph{changes} are communicated from the mapping node to the exploration and visualization nodes using a custom ROS message type. This change drastically decreases the time needed to generate or interpret the message. This is accomplished by finding a rectangular prism of the minimum and maximum limits of cells that may have changed during a particular measurement scan update. Publishing and subscribing to map changes provides an efficient means to transfer mapping information, independent of map size.

Another computational improvement key to autonomous exploration success is that only important and changing map information gains are updated. The expected information gain for a single candidate is updated ray-by-ray, where only the top $\hat{n}=5$ cells with the largest detection probabilities are considered using \refeqn{ProbOfFirstCell}. Since \refeqn{ProbMeas} is embedded in \refeqn{DiscExpEntropyRay}, the computational complexity for a ray with $n_{r}$ cells is $\mathcal O(n_{r}^2)$. Reducing the considered cells to $\hat{n}$ limits the computation to $\mathcal O(n_{p}^2)$ where $n_{p}\ll n_r$ in general. Furthermore, finding these $\hat{n}$ cells is computationally inexpensive; using a selection algorithm of the $n_{r}$ cells and a sorting algorithm of the $n_{p}$ cells, the computational complexity is amortized to $\mathcal O(n_r+\hat{n}\log(\hat{n}))$, which can be further approximated to $\mathcal O(n_r)$ assuming that $\hat{n}\ll n_r$. Thus, this entropy updating scheme scales well to varying sensor ranges and cell sizes. Furthermore, the information gains of poses far from any robot trajectory need not be updated between receding horizons.

\paragraph{Parameters and Resulting Maps}
The 3D mapping and exploration algorithms for three robots are simulated with several parameters, which are the same as those in Section \ref{sec:Compare2MapProjections} except the map limits are extended to $-55.0$ m to $55.0$ m in the x- and y-directions, and $0.0$ m to $1.5$ m in the z-direction, producing a total of $45,255,504$ grid cells with edge length $0.075$ m (dimensioned $1468\times1468\times21$). For the bump function, $\mathcal B_\text{max}=1$, $\mathcal B_\text{far}=0.1$, and $\beta=0.01$ are chosen. For bidding $\rho_\text{max}=3.0$ m is chosen.

In the simulation, three quadrotors explore the simulated environment of The George Washington University's (GWU) Science and Engineering Hall (SEH) for $10$ minutes while taking measurements. Each quadrotor is given an Asus Xtion depth sensor and Hokuyo LIDAR, where the sensor properties for the Asus Xtion are used with exploration expectations because they provide the vast majority of measurements. The building floor plan and Gazebo simulated environment are shown in Fig. \ref{fig:SEHEnvironment}. The 3D occupancy grid maps are shown in Fig. \ref{fig:sim3DMap}, and the corresponding 2D projected maps for exploration are shown in Fig. \ref{fig:sim2Dmaps} using the ROS visualization package Rviz. The full video of both maps is available at \href{https://youtu.be/OMn2c453oik}{\WriteBlue{https://youtu.be/OMn2c453oik}}.

\begin{figure}[!t]
\centering
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{SEH_cropped.png}
        		\caption{Floor Plan}
    	\end{subfigure}
	\hspace*{0.1\textwidth}
    	\begin{subfigure}[t]{0.4\columnwidth}
           	\centering
          	\includegraphics[width=\textwidth]{gazeboSEH.png}
        		\caption{Gazebo Model}
    	\end{subfigure}
	\caption{The SEH second floor plan (about $15,000$ sqft) is reconstructed with a Gazebo simulation environment.}
	\label{fig:SEHEnvironment}
\end{figure}

%	% trim={<left> <lower> <right> <upper>}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_1min_ss.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_2min_ss.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_3min_ss.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_4min_ss.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_5min_ss.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_6min_ss.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_7min_ss.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_8min_ss.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={26cm 10cm 24cm 10cm}, clip, width=\columnwidth]{multi_discount_raw_3D_9min_ss.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{3D Occupancy Grid Map of SEH Second Floor}
	\label{fig:sim3DMap}
\end{figure}

\begin{figure}[!t]
	\centering{
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_1min.jpg}
        		\caption{$1$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_2min.jpg}
        		\caption{$2$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_3min.jpg}
        		\caption{$3$ min}
    	\end{subfigure}
	}
	\centering{
	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_4min.jpg}
        		\caption{$4$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_5min.jpg}
        		\caption{$5$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_6min.jpg}
        		\caption{$6$ min}
    	\end{subfigure}
	}
	\centering{
   	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_7min.jpg}
        		\caption{$7$ min}
    	\end{subfigure}
 	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_8min.jpg}
        		\caption{$8$ min}
    	\end{subfigure}
	\hspace*{0.05\textwidth}
    	\begin{subfigure}[t]{0.25\columnwidth}
          	\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, width=\columnwidth]{multi_discount_raw_2D_9min.jpg}
        		\caption{$9$ min}
    	\end{subfigure}
	}
	\caption{2D Projected Occupancy Grid Map of SEH Second Floor}
	\label{fig:sim2Dmaps}
\end{figure}

%	
%	\begin{figure}
%	% trim={<left> <lower> <right> <upper>}
%		\centering{
%			\subfigure[$0$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_0min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$1$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_1min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$2$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_2min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$3$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_3min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$4$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_4min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$5$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_5min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$6$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_6min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$7$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_7min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\centering{
%			\subfigure[$8$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_8min.jpg}}
%			\hspace*{0.025\columnwidth}
%			\subfigure[$9$ min]{\includegraphics[trim={22cm 5cm 16cm 3.5cm}, clip, height=0.45\columnwidth]{multi_discount_raw_2D_9min.jpg}}
%		}
%		\vspace*{0.025\columnwidth}
%		\caption{2D Projected Occupancy Grid Map of SEH Second Floor}
%			\label{fig:sim2Dmaps}
%	\end{figure}

The resulting 3D occupancy grid shows a nearly-completed map after three quadrotors cooperatively explored over $10$ minutes, which is quantified with total map entropy from \refeqn{ShannonsEntropyMap}, shown in Fig. \ref{fig:simH}. An important observation is that the majority of map space was unreachable by any robot, so about $1.2\times10^7$ of the entropy metric could not be improved, regardless of mapping or exploration strategy.

Special attention had to be placed on parameter selection for the bump function and collision-avoidance. For the bump function, increasing the parameter $\beta$ narrows the bump, placing a stronger influence on nearby candidates. However, this choice corresponds to the bump function decreasing at a negligible rate beyond a close neighborhood of the robot, i.e., a large range of distances yield $\mathcal B\approx\mathcal B_\text{far}$. Hence, there is a tradeoff between prioritization of local movements and being able to differentiate the effects of distance on large trajectories.

When robots competed for future poses in a centralized auction framework, the repeated optimizations provided an effective multi-vehicle exploration policy. Between auctions, only a small set of candidates within the neighborhood of the last auction-winning candidate require consideration when updating expected information gains with \refeqn{ExpectedMeasRay} and avoiding collisions between robots using \refeqn{CollisionAvoidanceAmongRobots}, both of which modify the optimization of \refeqn{OptPoseMulti}. Since bidding is applied efficiently, its computation time is negligible compared with other parts of the exploration update such as computing the initial candidate information gains and robot cost maps.

	\begin{figure}
		\centering{
			\includegraphics[width=0.9\columnwidth]{multi_H.pdf}
		}
		\caption{Total 3D Map Cell Entropy}
		\label{fig:simH}
	\end{figure}

@@

Patrol is the continuous and repetitive observation of different regions within a larger environment. An effective patrol algorithm is particularly valuable for surveillance operations, especially when the robot members are incapable of measuring all regions of an environment from fixed poses. Here, we formulate cooperative patrol as an optimization problem, where expected map information gains are maximized cooperatively according to the methods outlined in Section \ref{sec:BiddingExploration}. However, the grid cells experience slow degradation over time, thereby modifying the expected map information gains that govern exploration. This way, different regions are revisited after some time passes. This method of cell degradation for cooperative robotic patrol is described next.

\subsection{Continuous-Time Markov Process for Cell Degradation}

The key idea to cell degradation is that as time progresses forward, cells become more uncertain, which causes the exploration algorithm to revisit these cells. All cells are degraded through a continuous-time Markov process at an equal rate, thereby creating a fair policy for revisiting regions that exploits the benefits of multi-vehicle exploration, such as following a receding horizon and optimizing information gain and travel time. Cell degradation is applied simply and uniformly to the entire 3D map for autonomous cooperative patrol. Since this analysis is valid for all grid cells, cell index notation is neglected for this analysis.

Consider that a single grid cell begins with probability $P(\mathbf{m}_{t_0})$ at time $t_0$ and degrades to $P(\mathbf{m}_{t_f})$ at time $t_f>t_0$. Suppose that as time progresses forward after $t_0$, the cell probability approaches a terminal value $P_\infty\in(0,1)$, i.e.,
\begin{align}
\label{eqn:DegradationQualification}
\lim_{t\rightarrow\infty}\begin{bmatrix}
P(\mathbf{m}_{t})
\\
P(\bar{\mathbf{m}}_{t})
\end{bmatrix}
=
\begin{bmatrix}
P_\infty
\\
1-P_\infty
\end{bmatrix}.
\end{align}
Let the degradation rate be $\lambda>0$ and matrix $A\in\Re^{2\times2}$ be defined as
\begin{align}
A=\lambda
\begin{bmatrix}
-(1-P_\infty) & P_\infty
\\
(1-P_\infty) & -P_\infty
\end{bmatrix}.
\end{align}
Then the first-order ordinary differential equation is expressed as
\begin{align}
\begin{bmatrix}
\dot{P}(\mathbf{m}_{t})
\\
\dot{P}(\bar{\mathbf{m}}_{t})
\end{bmatrix}
=
A
\begin{bmatrix}
P(\mathbf{m}_{t})
\\
P(\bar{\mathbf{m}}_{t})
\end{bmatrix}.
\end{align}
Hence, the state transition from $t_0$ to $t_f$ is
\begin{align}
\label{eqn:DegradeStateTransition}
\begin{bmatrix}
P(\mathbf{m}_{t_f})
\\
P(\bar{\mathbf{m}}_{t_f})
\end{bmatrix}
&=
\exp\braces{A(t_f-t_0)}
\begin{bmatrix}
P(\mathbf{m}_{t_0})
\\
P(\bar{\mathbf{m}}_{t_0})
\end{bmatrix},
\end{align}
which is illustrated with Fig. \ref{fig:MarkovDegradeContinuous}. Most importantly, \refeqn{DegradeStateTransition} satisfies \refeqn{DegradationQualification} as $t_f\rightarrow\infty$. Solving the top row of \refeqn{DegradeStateTransition} yields
\begin{align}
\label{eqn:CellDegradationScalar}
P(\mathbf{m}_{t_f})=P(\mathbf{m}_{t_0})\exp\braces{-\lambda (t_f-t_0)}+P_\infty(1-\exp\braces{-\lambda (t_f-t_0)}).
\end{align}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{markov_diagram_continuous.pdf}
\caption{The continuous-time Markov process for a single binary cell occupancy is illustrated. As time progresses, this process degrades the cell slowly toward $P_\infty.$}
\label{fig:MarkovDegradeContinuous}
\end{figure}

Applying degradation is computationally-inexpensive due to the simplicity of \refeqn{CellDegradationScalar}. For an arbitrary positive fixed time step, $\exp\braces{-\lambda (t_f-t_0)}$ needs only be calculated once and is multiplied to every map cell. Similarly, the second term of \refeqn{CellDegradationScalar}, namely $P_\infty(1-\exp\braces{-\lambda (t_f-t_0)})$, is simply added to every cell. For grid cells with probabilities far from $P_\infty$, the times to converge to this final degraded value increase, shown in Fig. \ref{fig:DegradeExamples}. Slow convergence of cells with probabilities close to $0$ or $1$ allows the robots to stop viewing these cells, giving the robots opportunities to visit different regions before returning.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{DegradeExamples.pdf}
\caption{The rate at which probabilities converge toward $P_\infty=0.4$ increases based on the difference magnitude of their initial values.}
\label{fig:DegradeExamples}
\end{figure}

In short, each grid cell is continuously degrading according to \refeqn{CellDegradationScalar} toward $P_\infty$. Only in the presence of measurements does the cell occupancy become well-known according to \refeqn{RayISMAnswer}--\refeqn{Unnormalized}. Cell degradation encourages the robot to revisit cells from the distant past using bidding-based multi-vehicle autonomous exploration to patrol the environment continuously. Adopting the receding horizon framework allows patrol to account for dynamic obstacles by quickly updating patrol strategies as map information changes.
